On the Minimum Core Mass for Giant Planet Formation at Wide Separations

### 2014-02-13 tex/PaperI/ms.tex
extra stevenson 82 reference for mu

The effect of mean molecular weight is also shown in \Fig{fig:tvsMcomp}.  A lower $\mu$ gives longer growth times, because more cooling is required to compress the atmosphere.  \textbf{This effect is intuitive since the atmospheric scale height $\propto 1/\mu$ is more extended for lower $\mu$.   The Bondi radius decreases as $\RB \propto \mu$ giving a smaller gravitational sphere of influence (and a weaker compression at $\RH$ when that is the more relevant scale).} For $\mu = 2.0$, which represents the idealized case of an H$_2$ atmosphere completely devoid of Helium, $t_{\rm run}$ increases by factors of $\sim 2 - 3$.  Thus fairly drastic changes in atmospheric composition are required for $\mu$ to significantly affect core accretion timescales. \textbf{In principle, changes in the mean molecular weight of the gas also affect the EOS, including $\delad$, but such effects are not considered here, see \S\ref{sec:EOS}.}

>>>>

The effect of mean molecular weight is also shown in \Fig{fig:tvsMcomp}.  A lower $\mu$ gives longer growth times, because more cooling is required to compress the atmosphere.  \textbf{This effect is both well established in core accretion studies \citep{stevenson82} and intuitive since the atmospheric scale height $\propto 1/\mu$ is more extended for lower $\mu$.   The Bondi radius decreases as $\RB \propto \mu$ giving a smaller gravitational sphere of influence (and a weaker compression at $\RH$ when that is the more relevant scale).} For $\mu = 2.0$, which represents the idealized case of an H$_2$ atmosphere completely devoid of Helium, $t_{\rm run}$ increases by factors of $\sim 2 - 3$.  Thus fairly drastic changes in atmospheric composition are required for $\mu$ to significantly affect core accretion timescales. \textbf{In principle, changes in the mean molecular weight of the gas also affect the EOS, including $\delad$, but such effects are not considered here, see \S\ref{sec:EOS}.}
